\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\linespread{1.1} % Adjust line spacing slightly

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}



%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% Suraj's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%
\documentTitle{Suraj Kumar}{
    \href{tel:+917367089724}{
      \raisebox{-0.05\height}{\faPhone} +91 7367089724} ~ | ~
    \href{mailto:surajkumar06174@gmail.com}{
      \raisebox{-0.15\height}{\faEnvelope} surajkumar06174@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/surajkr97/}{
      \raisebox{-0.15\height}{\faLinkedin} https://www.linkedin.com/in/surajkr97/} ~ | ~
    \href{https://github.com/surajkr97}{
      \raisebox{-0.15\height}{\faGithub} github.com/surajkr97/}
}

  %-------------------%
  % Professional Summary %
  %-------------------%
  \section{Professional Summary}
  Frontend Developer with experience in building scalable, \textbf{\textit{responsive web applications}} using modern UI/UX principles. Proven ability to collaborate with global teams and deliver solutions aligned with business goals. Open to remote opportunities with time zone flexibility.

  %--------%
  % Skills %
  %--------%

  %   \section{Skills}

  % \begin{multicols}{2}
  %   \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120pt]
  %     \item[\textbf{Frontend Development:}] HTML, CSS, JavaScript, React.js
  %     \item[\textbf{UI/UX Design Tools:}] Figma, Mockplus
  %     \item[\textbf{Styling Frameworks:}] Tailwind CSS, Bootstrap
  %     \item[\textbf{Developer Tools:}] VS Code, Git, Linux
  %   \end{itemize}
  % \end{multicols}

\section{Skills}
\begin{multicols}{2}
  \begin{itemize}[itemsep=2pt, parsep=1pt, leftmargin=15pt]
    \item \textbf{Frontend Development:} HTML5, CSS3, JavaScript (ES6+), React.js, JSX, React Router
    \item \textbf{Styling \& UI Frameworks:} Tailwind CSS, Responsive Design, Flexbox, Grid
    \item \textbf{Version Control \& Tools:} Git, GitHub, VS Code, Netlify
    \item \textbf{UI/UX \& Prototyping:} Figma, User Flow Design
  \end{itemize}
\end{multicols}


  %------------%
  % Projects %
  %------------%

  \section{Projects}

 \headingBf {\underline{\href{https://legendary-bonbon-8df4a1.netlify.app/}{RouterVault \(\nearrow\)}}}{March 2025}  \vspace{4pt}
\begin{resume_list}
    \item Built a multi-page web application using \textbf{React.js} and \textbf{React Router v6}, with nested routes and loader-based data fetching.
    \item Implemented secure \textbf{authentication} using \textbf{localStorage} to manage user sessions and restrict access to protected routes.
    \item Designed modular and reusable UI components like \texttt{Header}, \texttt{Hero}, \texttt{Footer}, and user authentication pages.
    \item Integrated a \textbf{\textit{live GitHub user search feature with React Router loaders}}, improving user interactivity.
    \item Prioritized responsive design and smooth navigation to ensure a seamless single-page application (SPA) experience.
\end{resume_list}

  
\headingBf {\underline{\href{https://moonlit-lolly-0ff123.netlify.app/}{Live Cricket Score \(\nearrow\)}}}{February 2025}  \vspace{4pt}
\begin{resume_list}
    \item Developed a responsive web app in \textbf{React.js} that fetches and displays real-time scores for ODI, T20, and Test matches.
    \item Styled components using \textbf{Tailwind CSS}, ensuring clean UI and cross-device responsiveness.
    \item Applied advanced UI interactions including \textbf{3D hover effects} on match cards to improve visual appeal.
    \item Handled loading states and errors gracefully to enhance user experience.
\end{resume_list}


\headingBf {\underline{\href{https://chipper-pika-ccd3fb.netlify.app/}{Password Generator \(\nearrow\)}}}{December 2024}  \vspace{4pt}
\begin{resume_list}
    \item Created a secure password generation tool using \textbf{React.js} with customizable options like length, symbols, and digits.
    \item Utilized \textbf{React Hooks} (\texttt{useState}, \texttt{useEffect}, \texttt{useRef}) for optimized state and side-effect handling.
    \item Focused on minimalistic design with intuitive controls for instant password creation.
\end{resume_list}


\headingBf {\underline{\href{https://calm-zuccutto-519f2d.netlify.app/}{iTask Manager \(\nearrow\)}}}{January 2023}  \vspace{4pt}
\begin{resume_list}
    \item Developed a full-featured task management app using \textbf{React.js} and \textbf{Tailwind CSS} with support for CRUD operations.
    \item Enabled persistent task storage using \textbf{localStorage}, ensuring data retention across sessions.
    \item Designed a clean, mobile-friendly UI for easy task addition, editing, and deletion.
\end{resume_list}

% \section{Additional Projects}

% \noindent
% \centering

% \textbf{\underline{\href{https://surajkr97.github.io/ShivamSecurities/}{Investment Services \(\nearrow\)}}} \hfill
% \textbf{\underline{\href{https://github.com/surajkr97/Js-Projects}{JavaScript Projects \(\nearrow\)}}}\hfill
% \textbf{\underline{\href{https://github.com/surajkr97/Expense-Tracker-App}{Expense Tracker App \(\nearrow\)}}} \hfill
% \textbf{\underline{\href{https://surajkr97.hashnode.dev/exploring-the-world-of-iot-from-robo-cars-to-robo-warrior?source=more_articles_bottom_blogs}{Hand Gesture Controlled Robot Car \(\nearrow\)}}}

  %------------%
  % Professional Experience %
  %------------%

  \section{Professional Experience}

  \headingBf{Frontend Developer Intern}{Cosmos Next Gen Tech Private Limited, \textit{October 2021 -- March 2022}}  \vspace{3pt}
  \begin{resume_list}
    \item \textit{Basic Styling and Layouts:} Assisted in creating responsive web pages using HTML, CSS, JavaScript, and React.
    \item \textit{UI Design with Figma:} Contributed to designing user interfaces in Figma to improve visual appeal and usability.
    \item \textit{Collaborated with Senior Developers:} Worked closely with experienced team members to learn and implement best practices in front-end development.
  \end{resume_list}

  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \headingBf{Uttarakhand Technical University}{August 2020 -- May 2024}
  \headingIt{B.Tech in Computer Science and Engineering}{Sudhowala, Dehradun}

  %----------------------------%
  % Achievements %
  %----------------------------%

  \section{Achievements}

  \begin{resume_list}
  \vspace{5pt}
    \item First runner-up in \textbf{\textit{Incubate india hackathon 2021 powered by Git Hub}} held in Tula’s Institute where we built a online virus tracker named as ScanIT.
    \item First runner-up in \textbf{\textit{Inter college Tech Talent Hackathon 2023}} which held in Haryana where we developed a memory game.
  \end{resume_list}

\end{document}